### 2018-08-06 article.tex
typo and small modifications

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{2-Category}

A \emph{strict} 2-category \catC is a category \emph{enriched over \textbf{Cat}}, the category of categories.

@@

In the following we'll always write $a, b, c$ for \emph{0-cells}, $f, g, h$ for \emph{1-cells} and $r, s, t$ for \emph{2-cells}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL 2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Monoidal 2-category}

A \emph{strict} monoidal 2-category $(\catC, \otimes)$ is a strict 2-category with

\begin{itemize}
\item a 2-bifunctor $\otimes: \catC \times \catC \to \catC$ such that on 2-cells $r, s, t, u$
\[
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
\]
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        QUANTALE DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quantale}

A quantale $\mathbb{Q}$, over a \emph{group}, is a monoidal category

\begin{itemize}
\item objects are elements of a lattice $L$
\item for all objects $(x, y)$ there is a morphism between $x$ and $y$ iff $x \succeq y$ in $L$.
\item a unit objet $e \in L$
\item a monoidal operator $\oplus: Q \times Q \to Q$
\end{itemize}

\noindent such that for all $x, y \in L$ and $\{x_i\}_i, \{y_i\}_i \subseteq L$
\begin{align}
x \oplus \bigvee y_i &= \bigvee x \oplus y_i \cr
\left(\bigvee x_i\right) \oplus y &= \bigvee x_i \oplus y
\end{align}

We require that for all objects $x$ of $\mathbb{Q}$, it exist an object $x^{-1}$ such that
\begin{align}
x \oplus x^{-1} &= e \cr
x^{-1} \oplus x &= e
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathbb{Q}$-enriched category}

A $\mathbb{Q}$-enriched category \catE is

@@

such that for all object $a$
\[
e \succeq \catE(a, a)
\]
for all objects (a, b, c)
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Monoidal $\mathbb{Q}$-enriched category}

$(E, \otimes)$ is strictly monoidal if
\[
\catE(a, b) \oplus \catE(a', b') \succeq \catE(a \otimes a', b \otimes b')
\]
and symmetric if
\[
e \succeq \catE(a \otimes b, b \otimes a)
\]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A \emph{groupoid} is a category where morphisms are invertible.
Let's define the following strict monoidal 2-groupoid \catC

\begin{itemize}
\item 0-cells are natural number $\mathbb{N}$
\item 1-cells are quantum circuits freely generated by $\circ$, $\otimes$ and $\{f_i\}_i$, a set of quantum circuits
\item 2-cells are quantum circuit transformations freely generated by $\circ$, $\otimes$ and $\{r_i\}_i$, a set of ransformations, such that $\forall r: f \Rightarrow g \in \{r_i\}_i, \exists r^{-1}: g \Rightarrow f \in \{r_i\}_i$
\[
r \circ r^{-1} = id_f
\]
\item the vertical composition is the usual transformations composition
\item the horizontal composition is the usual circuits composition
\item the 2-bifunctor is
\begin{itemize}
\item on 0-cell, $a \otimes b = a + b$
\item on $\catC(a, b)$, a functor $\catC(a, b) \otimes C(a', b') \to C(a + a', b + b')$
\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\catC(a, b)$ to $\mathbb{Q}$ homomorphism}

Let's define the following homomorphism $F$ from $\catC(a, b)$ to $\mathbb{Q}$. For all $f: a \to b \in \{f_i\}_i$
\[
F(f) \in L
\]
For all $r: f \Rightarrow g \in \{r_i\}_i$
\[
F(r) = F(f) \oplus F(g)^{-1}
\]

On 1-cells
\begin{align}
F(f \circ g) &\preceq F(f) \oplus F(g) \cr
F(f \otimes g) &\preceq F(f) \oplus F(g)
\end{align}

On 2-cells
\begin{align}
F(r \circ s) &= F(r) \oplus F(s) \cr
F(r \otimes s) &= F(r) \oplus F(s) \cr
F(r \bullet s) &= F(r) \oplus F(s)
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}
Note that because
\[
F(r: f \Rightarrow g) = F(f) \oplus F(g)^{-1}
\]
then
\begin{align}
F(r: f \Rightarrow f) &= F(f) \oplus F(f)^{-1} \cr
&= e
\end{align}
that is
\begin{align}
\forall f, F(id_f) = e
\end{align}
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
Given two transformations $r, s: f \Rightarrow g$, then $F(r) = F(s)$.

\begin{proof}
The set of all possible transformation is freely generated by $\{r_i\}_i$, $\bullet$, $\circ$ and $\otimes$ so both $r$ and $s$ can be written
\begin{align}
r &= r_1 \odot r_2 \odot r_3 \odot \cdots \odot r_n \cr
s &= s_1 \odot s_2 \odot s_3 \odot \cdots \odot s_m
\end{align}
with $\odot \in \{\bullet, \circ, \otimes\}$ and for all i
\begin{align}
r_i &\in \{f_i\}_i \cr
s_i &\in \{f_i\}_i
\end{align}
If $n = 1$ then $r \in \{f_i\}_i$, so $F(r) = F(f) \oplus F(g)^{-1}$.
Otherwise
\begin{align}
F(r) &= F(r_1 \odot r_2 \odot \cdots \odot r_n) \cr
&= F(r_1) \oplus F(r_2) \oplus \cdots \oplus F(r_n) \cr
&= F(f \Rightarrow h_1) \oplus F(h_1 \Rightarrow h_2) \oplus \cdots \oplus F(h_n \Rightarrow g) \cr
&= F(f) \oplus F(h_1)^{-1} \oplus F(h_1) \oplus F(h_2)^{-1} \oplus \cdots \oplus F(h_n) \oplus F(g)^{-1}
\end{align}
A easy inductive proof can show us that
\[
F(f) \oplus F(h_1)^{-1} \oplus F(h_1) \oplus F(h_2)^{-1} \oplus F(h_2) \oplus \cdots \oplus F(h_n) \oplus F(g)^{-1} = F(f) \oplus F(g)^{-1}
\]
The same is true for $s$, so
\[
F(r) = F(s) = F(f) \oplus F(g)^{-1}
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all transformations $r: f \Rightarrow g$, then $F(r) = F(f) \oplus F(g)^{-1}$.
Note that the definition of $F$ gives that only for $r \in \{f_i\}_i$.
\end{corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
The following category $\catC(\mathbb{Q})$ is a $\mathbb{Q}$-category
\begin{itemize}
\item A set of objects which are the 1-cells of $\catC$
\item For all objects $(f, g)$
\end{itemize}
\[
\catE(f, g) = \begin{cases} {\rm if~} f \Rightarrow g \in \catC, &F(f \Rightarrow g) \cr {\rm otherwise~} &\top \end{cases}
\]
With $\top \in Q$ such that for all $x \in \mathbb{Q}$
\[
x \preceq \top
\]

\begin{proof}
For all 1-cells $(f, g)$, if it exists a unique transformation $f \Rightarrow g$, then
\begin{align}
\catE(f, g) &= F(f \Rightarrow g) \in \mathbb{Q} \cr
&= F(f) \oplus F(g)^{-1}
\end{align}
otherwise we already have $\catE(f, g) = \top \in \mathbb{Q}$.
For all 1-cell $f$, we know that there is a identity transformation $f \Rightarrow f$ and
\begin{align}
\catE(f, f) &= F(id_f) \cr
&= F(f \Rightarrow f)\cr
&= F(f) \oplus F(f)^{-1} \cr
&= e
\end{align}
Finally, for all 1-cells $(f, g, h)$ such that there exists $r: f \Rightarrow g$ and $s: g \Rightarrow h$ in $\catC$, then the homomorphism $F$ give us
\begin{align}
\catE(f, h) &= F(f \Rightarrow h) \cr
&= F(s\circ r) \cr
&= F(s) \oplus F(r) \cr
&= F(g \Rightarrow h) \oplus F(f \Rightarrow g) \cr
&= \catE(g, h) \oplus \catE(f, g)
\end{align}
If either $r$ or $s$ doesn't exists in $\catC$ then
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]
become
\[\begin{matrix}
&\catE(b, c) \oplus \top &\succeq \top \cr
{\rm or~} &\top \oplus \catE(a, b) &\succeq \top \cr
{\rm or~} &\top \oplus \top &\succeq \top
\end{matrix}\]
which is still true.
\end{proof}
\end{proposition}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[2-Category]
A \emph{strict} 2-category \catC is a category \emph{enriched over \textbf{Cat}}, the category of categories.

@@

In the following we'll always write $a, b, c$ for \emph{0-cells}, $f, g, h$ for \emph{1-cells} and $r, s, t$ for \emph{2-cells}.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL 2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[Monoidal 2-category]
A \emph{strict} monoidal 2-category $(\catC, \otimes)$ is a strict 2-category with

\begin{itemize}
\item a 2-bifunctor $\otimes: \catC \times \catC \to \catC$ such that on 2-cells $r, s, t, u$
\[
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
\]
\end{itemize}
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        QUANTALE DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[Quantale $\mathbb{Q}$]
A quantale is a \emph{lattice} with a binary operator such that for all elements of the lattice $x, y$ and $\{x_i\}_i, \{y_i\}_i$
\begin{align}
x \oplus \bigvee y_i &= \bigvee x \oplus y_i \cr
\left(\bigvee x_i\right) \oplus y &= \bigvee x_i \oplus y
\end{align}

We require that for all $x$, it exist $x^{-1}$ such that
\begin{align}
x \oplus x^{-1} &= e \cr
x^{-1} \oplus x &= e
\end{align}

Such a quantale can be seen as a monoidal category over a \emph{group}.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[$\mathbb{Q}$-enriched category]
A $\mathbb{Q}$-enriched category \catE is

@@

such that for all object $a$
\[
e \succeq \catE(a, a)
\]
for all objects (a, b, c)
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL Q-ENRICHED CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[Monoidal $\mathbb{Q}$-enriched category]
$(E, \otimes)$ is strictly monoidal if
\[
\catE(a, b) \oplus \catE(a', b') \succeq \catE(a \otimes a', b \otimes b')
\]
and symmetric if
\[
e \succeq \catE(a \otimes b, b \otimes a)
\]
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
A \emph{groupoid} is a category where morphisms are invertible.
Let's define the following strict monoidal 2-groupoid \catC

\begin{itemize}
\item 0-cells are natural number $\mathbb{N}$
\item 1-cells are quantum circuits freely generated by $\circ$, $\otimes$ and $\{f_i\}_i$, a set of quantum circuits
\item 2-cells are quantum circuit transformations freely generated by $\circ$, $\otimes$ and $\{r_i\}_i$, a set of ransformations, such that $\forall r: f \Rightarrow g \in \{r_i\}_i, \exists r^{-1}: g \Rightarrow f \in \{r_i\}_i$
\[
r \circ r^{-1} = id_f
\]
\item the vertical composition is the usual transformations composition
\item the horizontal composition is the usual circuits composition
\item the 2-bifunctor is
\begin{itemize}
\item on 0-cell, $a \otimes b = a + b$
\item on $\catC(a, b)$, a functor $\catC(a, b) \otimes C(a', b') \to C(a + a', b + b')$
\end{itemize}
\end{itemize}
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[$\catC(a, b)$ to $\mathbb{Q}$ homomorphism]
Let's define the following homomorphism $F$ from $\catC(a, b)$ to $\mathbb{Q}$. For all $f: a \to b \in \{f_i\}_i$
\[
V(f) \in \mathbb{Q}
\]
For all $r: f \Rightarrow g \in \{r_i\}_i$
\[
V(r) = V(f) \oplus V(g)^{-1}
\]

On 1-cells
\begin{align}
V(f \circ g) &\preceq V(f) \oplus V(g) \cr
V(f \otimes g) &\preceq V(f) \oplus V(g)
\end{align}

On 2-cells
\begin{align}
V(r \circ s) &= V(r) \oplus V(s) \cr
V(r \otimes s) &= V(r) \oplus V(s) \cr
V(r \bullet s) &= V(r) \oplus V(s)
\end{align}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}
Note that because
\[
V(r: f \Rightarrow g) = V(f) \oplus V(g)^{-1}
\]
then
\begin{align}
V(r: f \Rightarrow f) &= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
that is
\begin{align}
\forall f, V(id_f) = e
\end{align}
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
Given two transformations $r, s: f \Rightarrow g$, then $V(r) = V(s)$.

\begin{proof}
The set of all possible transformation is freely generated by $\{r_i\}_i$, $\bullet$, $\circ$ and $\otimes$ so both $r$ and $s$ can be written
\begin{align}
r &= r_1 \odot r_2 \odot r_3 \odot \cdots \odot r_n \cr
s &= s_1 \odot s_2 \odot s_3 \odot \cdots \odot s_m
\end{align}
with $\odot \in \{\bullet, \circ, \otimes\}$ and for all i
\begin{align}
r_i &\in \{f_i\}_i \cr
s_i &\in \{f_i\}_i
\end{align}
If $n = 1$ then $r \in \{f_i\}_i$, so $V(r) = V(f) \oplus V(g)^{-1}$.
Otherwise
\begin{align}
V(r) &= V(r_1 \odot r_2 \odot \cdots \odot r_n) \cr
&= V(r_1) \oplus V(r_2) \oplus \cdots \oplus V(r_n) \cr
&= V(f \Rightarrow h_1) \oplus V(h_1 \Rightarrow h_2) \oplus \cdots \oplus V(h_n \Rightarrow g) \cr
&= V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus \cdots \oplus V(h_n) \oplus V(g)^{-1}
\end{align}
A easy inductive proof can show us that
\[
V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus V(h_2) \oplus \cdots \oplus V(h_n) \oplus V(g)^{-1} = V(f) \oplus V(g)^{-1}
\]
The same is true for $s$, so
\[
V(r) = V(s) = V(f) \oplus V(g)^{-1}
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all transformations $r: f \Rightarrow g$, then $V(r) = V(f) \oplus V(g)^{-1}$.
Note that the definition of $F$ gives that only for $r \in \{f_i\}_i$.
\end{corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
The following category $\catC(\mathbb{Q})$ is a $\mathbb{Q}$-category
\begin{itemize}
\item A set of objects which are the 1-cells of $\catC$
\item For all objects $(f, g)$
\end{itemize}
\[
\catE(f, g) = \begin{cases} {\rm if~} f \Rightarrow g \in \catC, &V(f \Rightarrow g) \cr {\rm otherwise~} &\top \end{cases}
\]
With $\top \in Q$ such that for all $x \in \mathbb{Q}$
\[
x \preceq \top
\]

\begin{proof}
For all 1-cells $(f, g)$, if it exists a unique transformation $f \Rightarrow g$, then
\begin{align}
\catE(f, g) &= V(f \Rightarrow g) \in \mathbb{Q} \cr
&= V(f) \oplus V(g)^{-1}
\end{align}
otherwise we already have $\catE(f, g) = \top \in \mathbb{Q}$.
For all 1-cell $f$, we know that there is a identity transformation $f \Rightarrow f$ and
\begin{align}
\catE(f, f) &= V(id_f) \cr
&= V(f \Rightarrow f)\cr
&= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
Finally, for all 1-cells $(f, g, h)$ such that there exists $r: f \Rightarrow g$ and $s: g \Rightarrow h$ in $\catC$, then the homomorphism $F$ give us
\begin{align}
\catE(f, h) &= V(f \Rightarrow h) \cr
&= V(s\circ r) \cr
&= V(s) \oplus V(r) \cr
&= V(g \Rightarrow h) \oplus V(f \Rightarrow g) \cr
&= \catE(g, h) \oplus \catE(f, g)
\end{align}
If either $r$ or $s$ doesn't exists in $\catC$ then
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]
become
\[\begin{matrix}
&\catE(b, c) \oplus \top &\succeq \top \cr
{\rm or~} &\top \oplus \catE(a, b) &\succeq \top \cr
{\rm or~} &\top \oplus \top &\succeq \top
\end{matrix}\]
which is still true.
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 3        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
$\catC(\mathbb{Q})$ is strictly symmetric monoidal with $\otimes$, the 2-functor of $\catC$.

\begin{proof}
The monoidal structure is immediate using the fact that
\[
V(r) \oplus V(s) \succeq V(r \otimes s)
\]
that is
\[
V(r: f \Rightarrow g) \oplus V(s: f' \Rightarrow g') = V(r \otimes s: f \otimes f' \Rightarrow g \otimes g')
\]
so
\[
\catE(f, g) \oplus \catE(f', g') = \catE(f \otimes f', g \otimes g')
\]
For the symmetry, we use the fact that $V(f \Rightarrow g) \oplus V(g \Rightarrow f) = e$
\begin{align}
\catE(f \otimes g, g \otimes f) &= V(f \otimes g \Rightarrow g \otimes g) \cr
&= V(f \Rightarrow g \otimes g \Rightarrow f) \cr
&\preceq V(f \Rightarrow g) \oplus V(g \Rightarrow f) \cr
&= V(f) \oplus V(g)^{-1} \oplus V(g) \oplus V(f)^{-1} \cr
&= e
\end{align}
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 3 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
Given $s: f \Rightarrow g$ a transformation, and $s^{-1}: g \Rightarrow f$ the inverse transformation
\[
V(s \otimes s^{-1}) = e
\]
\end{corollary}
